### 2018-01-16 circuit-elements/paper.tex
measurements for lenses lab

@@

	The relationship was investigated using a multimeter, a thermistor, a thermometer and a thermal flask for maintaining the thermistor at different temperatures, set up as shown:

@@

	The temperature of the thermistor was decreased by adding cold water to the thermal flask.

>>>>

	Circuit components may be grouped into linear and nonlinear. In linear components, such as resistors, capacitors, and some inductors, the signal obeys the principle of superposition; such components process electronic signals without distorting them. Nonlinear circuit components do not have a linear relationship between current and potential, and thus may distort electrical signals.

@@

	The relationship was investigated using a multimeter, a thermistor, a thermometer and a thermal flask for maintaining the thermistor at different temperatures, set up as shown below. The temperature of the thermistor was decreased by adding cold water to the thermal flask.

@@
